On Secure Delegation of SampBQP with a Classical Client

### 2020-03-22 qpip.tex
Rename VHam
Reparametrize QPIP1 SampBQP proof

\def\GS{\mathsf{GS}}
\nc{\PiGS}{\ensuremath{\Pi_\GS}}
\nc{\VGS}{\ensuremath{V_\GS}}
\nc{\PGS}{\ensuremath{P_\GS}}
\nc{\PGSstar}{\ensuremath{P_\GS^*}}
\nc{\cVGS}[1]{\ensuremath{\cV_{\GS,#1}}}
\nc{\cPGS}[1]{\ensuremath{\cP_{\GS,#1}}}

@@

\def\GS{\mathsf{GS}}

@@

	\begin{enumerate}
		\item The honest prover prepares $M$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $N$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cA_{\GS}(\rho_i)$.
			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
			\item Otherwise, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-hm$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I:p_j=\cA_\GS(\rho_j)<\frac{1}{2}-2h}$ and its complement. \Ethan{TODO import and use the right ``given" command.}

	First suppose $j\in J$
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
	then clearly $\Prob{Z>\frac{m}{2}-hm}<\Prob{Y>\frac{m}{2}-hm}$.
	By Chernoff bound, we have
	$$\Prob{Y-(\frac{1}{2}-2\varepsilon)m\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
	where $\mu_y=mp_y$ and $\delta=\frac{2h}{1-4h}$.

	Summing up all these terms, we get
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda)$$
	So this case doesn't get accepted often enough to matter.

	Now, for the other case, $j\notin J$.
	$$P[\cA_\GS(\phi)=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}$$
	we then have
	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\frac{1}{T^\lambda}.$$

	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{at least I think we do. Need theorem.}
	$$\braket{\rho_i|\phi_{C'(x)}}>1-O(T^{-\lambda})$$
	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close to as if the ground state is measured.}

	The probability of measuring $t<T$ on the clock register of $\ket{\psi_{C'(x)}}$ is $\varepsilon$,
	so the data register has $1-\varepsilon$ probability to be $C(x)$ at this point.

	The soundness errors incurred at each step is at most $O(T^{-\lambda})$, so the conclusion follows.
\end{prf}

>>>>

\def\GS{\mathsf{Ham}}
\nc{\PiGS}{\ensuremath{\Pi_\GS}}
\nc{\VGS}{\ensuremath{V_\GS}}
\nc{\PGS}{\ensuremath{P_\GS}}
\nc{\PGSstar}{\ensuremath{P_\GS^*}}
\nc{\cVGS}[1]{\ensuremath{\cV_{\GS,#1}}}
\nc{\cPGS}[1]{\ensuremath{\cP_{\GS,#1}}}

@@

@@

	\begin{enumerate}
		\item The honest prover prepares $M$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $N$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
			\item Otherwise, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-hm$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	Now we separate the $\rho_j$ into two categories: $J=\set{j\in I|p_j=\cV_\GS(\rho_j)<\frac{1}{2}-2h}$ and its complement.

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
	then clearly $\Prob{Z\geq\frac{m}{2}-hm}<\Prob{Y\geq\frac{m}{2}-hm}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-hm}=\Prob{Y-\mu\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
	where $\mu=mp_y=\frac{m}{2}-2hm$ and $\delta=\frac{2h}{1-4h}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda)$$

	Now, for the other case, $j\notin J$.
	$$\Prob{\cV_\GS(\phi)=acc}>\frac{1}{2}-2h\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\poly(\varepsilon)$$
	we then have
	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\poly(\varepsilon).$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain
	$$\braket{\rho_i|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
	By a standard fidelity argument, the measurement results on $\rho_i$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.

	The probability of measuring $t<T$ on the clock register of $\ket{\phi_{C'(x)}}$ is $\poly(\varepsilon)$ due to the padding,
	so the data register has $1-\poly(\varepsilon)$ probability to be $C(x)$ at this point.

	The soundness errors incurred at each step is at most $\poly(\varepsilon)$, so the conclusion follows.
\end{prf}
